Draft Exploration

### 2020-05-06 draft_exploration.Rmd
regression discontinuity in shiny

signed_by_year <- master %>%
  mutate(signed_numeric = ifelse(signed == "Y", 1, 0)) %>%
  group_by(year) %>%
  summarize(percent_signed = sum(signed_numeric) / n(),
            drafted = n(),
            signed = sum(signed_numeric))

signed_by_year %>%
  ggplot(aes(year, percent_signed)) +
  geom_point(color = "dodgerBlue4") +
  geom_line(color = "dodgerBlue") +
  theme_light() +
  labs(
    x = "Year",
    y = "Percent of Picks Signed"
  )

signed_by_year_hs <- master %>%
  filter(source == "H" & draft_round >= 20 & draft_round <= 40) %>%
  mutate(signed_numeric = ifelse(signed == "Y", 1, 0)) %>%
  group_by(year) %>%
  summarize(percent_signed = sum(signed_numeric) / n(),
            drafted = n(),
            signed = sum(signed_numeric))

signed_by_year_hs %>%
  ggplot(aes(year, percent_signed)) +
  geom_point(color = "dodgerBlue4") +
  geom_line(color = "dodgerBlue") +
  theme_light() +
  labs(
    x = "Year",
    y = "Percent of Picks Signed",
    title = "Signability of High School Picks Over Time"
  )
```

>>>>

signed_by_year <- master %>%
  mutate(signed_numeric = ifelse(signed == "Y", 1, 0)) %>%
  group_by(year) %>%
  summarize(percent_signed = sum(signed_numeric) / n(),
            drafted = n(),
            signed = sum(signed_numeric)) %>%
  mutate(period = ifelse(year <= 2011, "Pre-2012", "2012-Onward"))

signed_by_year %>%
  ggplot(aes(year, percent_signed)) +
  geom_point(aes(color = period)) +
  geom_smooth(formula = y ~ x + x^2, aes(color = period)) +
  theme_light() +
  labs(
    x = "Year",
    y = "Percent of Picks Signed",
    title = "Trends in Signability of Draft Picks",
    subtitle = "Before and after the draft was shortened to 40 rounds in 2011",
    color = "Period"
  )

signed_by_year_hs <- master %>%
  filter(source == "H") %>%
  mutate(signed_numeric = ifelse(signed == "Y", 1, 0)) %>%
  group_by(year) %>%
  summarize(percent_signed = sum(signed_numeric) / n(),
            drafted = n(),
            signed = sum(signed_numeric)) %>%
  mutate(period = ifelse(year <= 2011, "Pre-2012", "2012-Onward"))

signed_by_year_hs %>%
  ggplot(aes(year, percent_signed)) +
  geom_point(color = "dodgerBlue4") +
  geom_line(color = "dodgerBlue") +
  theme_light() +
  labs(
    x = "Year",
    y = "Percent of Picks Signed",
    title = "Signability of High School Picks Over Time"
  )

signed_by_year_hs %>%
  ggplot(aes(year, percent_signed)) +
  geom_point(aes(color = period)) +
  geom_smooth(formula = y~x+x^2, se = FALSE, aes(color = period)) +
  theme_light() +
  labs(
    x = "Year",
    y = "Percent of Picks Signed",
    title = "Trends in Signability of High School Picks",
    subtitle = "Before and after the draft was shortened to 40 rounds in 2011"
  )
```

```{r, echo = FALSE}

# making function for signability by round regression discontinuity with
# variable rounds and player source.

draft_signability <- function(min_round = 1, max_round = 100, player_source = c("H", "C")) {

signed_by_year <- master %>%
  filter(draft_round >= min_round & draft_round <= max_round) %>%
  filter(source %in% player_source) %>%
  mutate(signed_numeric = ifelse(signed == "Y", 1, 0)) %>%
  group_by(year) %>%
  summarize(percent_signed = sum(signed_numeric) / n(),
            drafted = n(),
            signed = sum(signed_numeric)) %>%
  mutate(period = ifelse(year <= 2011, "Pre-2012", "2012-Onward"))

signed_by_year %>%
  ggplot(aes(year, percent_signed)) +
  geom_point(aes(color = period)) +
  geom_smooth(formula = y ~ x + x^2, aes(color = period)) +
  theme_light() +
  labs(
    x = "Year",
    y = "Percent of Picks Signed",
    title = "Trends in Signability of Draft Picks",
    subtitle = "Before and after the draft was shortened to 40 rounds in 2011",
    color = "Period"
  )

draft_signability(min_round = 1)
```
